### 2014-05-14 research/paper/main/article.tex
update 6.19 13th may

\subsection{Parameters used}

For the low \reynoldsnumber\ tests, $\reynoldsnumber=165$ was maintained as it was pointed out by \citet{Sheard2009} and \citet{Tong2008} that the three-dimensional transition for a square cylinder occurs at approximately \reynoldsnumber=160. $F_0$ was kept at $0.4937$ which was obtained by scaling the value used by \citet{Joly2012} with the amplitude ratios of the lift forces obtained at the different Reynolds numbers.

The angular vortex shedding frequency $\omega_s$, was set to $0.98$ which was obtained by performing a power spectral analysis of the stationary data at $0^\circ$. Stationary $C_y$ data were obtained at different angles of attack ranging from $0^\circ$ to $16^\circ$. The average power was obtained by using equation \ref{power}, and the averaging was done over no less than 20 galloping periods. Predictions of power output at $\reynoldsnumber=22300$ were obtained using the coefficients for curve fitting $C_y$ (Table (\ref{table:cy-coefficients})) from \citet{Parkinson1964}, in order to provide a comparison between high and low Reynolds numbers. The mass ratio $m^*$ was kept at 1163 for $\reynoldsnumber=22300$ (Similar to \citet{Parkinson1964}) and $m^*=20$ for \reynoldsnumber=165. These parameters were used throughout this study unless otherwise specified.

The stationary data and the fluid-structure interaction (FSI) data were obtained using a high-order spectral element routine to simulate the two-dimensional laminar flow.  Simulations involving fluid structure interaction (FSI) were used to provide additional validation of the QSS model. The inlet was placed $20D$ while the outlet situated $60D$ away from the centroid of the body. The side boundaries were placed $20D$ away from the centroid of the body where $D$ was kept as unity throughout this study. The Navier--Stokes equations were solved in an accelerated frame of reference attached to the moving body along with the body equation of motion given in equation \ref{equationofmotion}. A three-step time splitting scheme together with high-order Lagrangian polynomials were used to obtain the solution. The details of the method can be found in \citet{Thompson2006,Thompson1996a}. This code has been very well validated in a variety of fluid-structure interaction problems \citep{Leontini2007a,Griffith2011,Leontini2011,Leontini2013}.

The computational domain consists of 690 quadrilateral macro elements where the majority of the elements were concentrated near the square section. A freestream condition was given to the inlet, top and bottom boundaries and the normal velocity gradient was set to zero at the outlet. A convergence study was performed by changing the order of the polynomial ($p$-refinement) at $U^*=40$ and $\reynoldsnumber=165$. A $9^{th}$ order polynomial together with a time step of $\Delta tU/D=0.001$ was sufficient to ensure an accuracy of $2\%$ with regards to amplitude of oscillation.

>>>>

 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \section{Results}
 \label{sec:results}

 \input{../figure/uncollapsed_data}
 \input{../figure/collapsed_data}

  \input{../figure/m_star_collapsed}
  \input{../figure/mstar_parkinson}
